\tw: Building a Xanalogical System in Ten Days

### 2003-02-12 papers/hypertext2003/paper.tex
Fixed wording, and fixed a reference.
Added a reference chain diagram.

\documentclass{acm_proc_article-sp}

@@

Keeping with the Xanadu model, \tw \ separates documents from the text they contain.
There are two types of data objects in \tw:  documents and chunks.
A chunk contains a raw block of contiguous text, while a document is a list of reference to text chunks.
Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.
Quote clipboards, like documents, contain a list of references.
However, to support showing the context of a quote, the references are not to chunks, but to the context documents themselves.
The chunks associated with a quote are only resolved when the quote is used as part of a new document.

@@

\section{Acknowledgements}
Thanks are due to Ted Nelson and Jim Whitehead for their contributions to interesting xanalogical discussions over the past year. ``Xanadu'' is a trademark of Ted Nelson.  To prevent confusion, the generic terms ({\it e.g.}, xanalogical) have been used wherever possible.

>>>>

\documentclass{acm_proc_article-sp}
\usepackage{graphs}

@@

\subsubsection{Data Model}
Keeping with the Xanadu model, \tw \ separates documents from the text they contain.
There are two types of data objects in \tw:  documents and chunks.
A chunk contains a raw block of contiguous text, while a document is a list of reference to text chunks.
Some of the referenced chunks in a document may have been created at the same time as the document (for new text in the document), while others may be part of quotes taken from other documents.

Each reference in a document contains a pointer to text chunk region and an optional pointer to a document context region.
The document context pointer tracks which document the material was quoted from and is used for quote reference chasing.
If a document refers to a new text chunk that has not appeared in any previous documents, the document context pointer is omitted:  such chunks are not part of quotes and have no references that can be chased.
With this two-pointer model, we can distinguish ``original'' material in a document from quoted material and support recursive reference chasing.
When following a quote reference, a chain of referneces may need to be chased before the original context of the text is found.

For example, suppose that document $A$ quotes a block of text from $B$, and that block contains a quote original material, residing in chunk $k$, from document $C$.  
$A$'s reference will contain both a pointer to the text chunk $k$ and to the document context $B$.  
$B$'s reference will point to both chunk $k$ and document $C$.  
At the end of this reference chain, $C$'s reference will point only to $k$.

\begin{figure*}[t]
\begin{center}

\begin{graph}(8,4)(-4,-1.65)
\graphnodesize{0.6}
\graphnodecolour{1}
\opaquetextfalse

\rectnode{A}[1.5,2](-6,0)[\fillednodesfalse]     
\autonodetext{A}[n]{Document $A$}
\roundnode{kInAAnchor}(-5.45,.25)[\graphnodecolour{0}\graphnodesize{0.1}]
\rectnode{AQuote}[1.5,0.75](-6,.25)[\graphnodecolour{0.5}]  
\rectnode{kInA}[1.5,0.5](-6,.25)[\graphnodecolour{0.85}]

\rectnode{B}[1.5,2](-2,0)[\fillednodesfalse]
\autonodetext{B}[s]{Document $B$}
\roundnode{kInBAnchor}(-1.45,-.5)[\graphnodecolour{0}\graphnodesize{0.1}]
\rectnode{AQuoteInB}[1.5,0.75](-2,-.5)[\graphnodecolour{0.5}]
\rectnode{BQuote}[1.5,0.5](-2,-.5)[\graphnodecolour{0.85}]

\rectnode{C}[1.5,2](2,0)[\fillednodesfalse]      
\autonodetext{C}[n]{Document $C$}
\rectnode{kInC}[1.5,1](2,0)[\graphnodecolour{.85}]
\rectnode{BQuoteInC}[1.5,0.5](2,.125)[\graphnodecolour{0.85}]

\rectnode{k}[1.5,1](6,0)[\graphnodecolour{.85}]      
\autonodetext{k}[n]{Chunk $k$}

\diredge{AQuote}{AQuoteInB}[\graphlinedash{4 4}\grapharrowtype{2}]
\dirbow{kInAAnchor}{k}{0.17}[\grapharrowtype{1}]

\diredge{BQuote}{BQuoteInC}[\graphlinedash{4 4}\grapharrowtype{2}]
\dirbow{kInBAnchor}{k}{-0.17}[\grapharrowtype{1}]

\diredge{kInC}{k}[\grapharrowtype{1}]

\end{graph}

\caption{An example reference chain.  Dotted arrows represent document pointers, and solid arrows represent chunk pointers.  Light gray regions represent text from chunk $k$.  Dark gray regions in $A$ and $B$ represent portions of $A$'s quote from $B$ that do not come from chunk $k$ (other chunks are omitted from this diagram for clarity).}
\label{fig:referenceChain}

\end{center}

\end{figure*}

Quote clipboards, like documents, contain a list of references.
However, to support showing the context of a quote, the references are not to chunks, but to the context documents themselves.
The chunks associated with a quote are only resolved when the quote is used as part of a new document.

@@

\section{Acknowledgements}
Thanks are due to Ted Nelson and Jim Whitehead for their contributions to interesting xanalogical discussions over the past year. ``Xanadu'' is a trademark of Ted Nelson.  To prevent confusion, the generic terms ({\it e.g.}, xanalogical system) have been used wherever possible.
